Embedding to Reference t-SNE Space Adresses Batch-Effects in Single-Cell Classification

### 2019-06-13 paper/transfer_learning.tex
Fix number of neighbors for initialization to 10

For each new data point, we first estimate its distance to each of the data instances in the reference data set. We initialize the position of the data point in embedding space to the median embedding position of its $k$ nearest neighbors from the reference data set. While we found the algorithm to be robust to choices of $k$, we use $k=25$ in our experiments.

@@

\begin{figure}[htbp]
\includegraphics[width=\textwidth]{figures/optimization_retina.pdf}
\caption{Comparison of data placement by nearest neighbors approach from Kobak and Berens~\cite{art_of_using_tsne} and optimized placement by our algorithm. {\bf (a)} Data points are placed to the median position of their 25 nearest neighbors in the reference set. {\bf (b)} Point positions are optimized, revealing a different, more dispersed placement that better reflects the variety of cells in the secondary data set.}
\label{fig:optimization}
\end{figure}

>>>>

For each new data point, we first estimate its distance to each of the data instances in the reference data set. We initialize the position of the data point in embedding space to the median embedding position of its $k$ nearest neighbors from the reference data set. While we found the algorithm to be robust to choices of $k$, we use $k=10$ in our experiments.

@@

\begin{figure}[htbp]
\includegraphics[width=\textwidth]{figures/optimization_retina.pdf}
\caption{Comparison of data placement by nearest neighbors approach from Kobak and Berens~\cite{art_of_using_tsne} and optimized placement by our algorithm. {\bf (a)} Data points are placed to the median position of their 10 nearest neighbors in the reference set. {\bf (b)} Point positions are optimized, revealing a different, more dispersed placement that better reflects the variety of cells in the secondary data set.}
\label{fig:optimization}
\end{figure}
